Identification of protoneutron star g-modes in gravitational-wave data

### 2020-09-03 simulations.tex
update

To tune the parameters of the algorithm, we use two sets of 25 models
in the range of initial stellar masses
$M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$ simulated with the two codes.
They were carried out using six equations of state (EOSs).  They are
complemented by a set of 7 two-dimensional axisymmetric models
consisting of stellar core collapse of five stars with zero-age
main-sequence masses of $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the EOS of
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
(GShen) for the one with $M_{\mathrm{ZAMS}} = 15 \, \Msol$ (see Table
\ref{Tab:2dSimList} for a list of models).  To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}.  It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.

>>>>

We use two sets of 25 models in the range of initial stellar masses
$M_{\mathrm{ZAMS}} = 11.2 - 75 \, \Msol$ simulated with the two codes.
They were carried out using six equations of state (EOSs).
In addition to these simulations data we have considered 8 waveforms.
7 of them are from two-dimensional axisymmetric models
consisting of stellar core collapse of five stars with zero-age
main-sequence masses of $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the EOS of
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
(GShen) for the one with $M_{\mathrm{ZAMS}} = 15 \, \Msol$ (see Table
\ref{Tab:2dSimList} for a list of models).  To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}.  It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.
